Timeliness of security updates for Android

### 2014-08-11 securityupdates.tex
Consistently use XXX rather than ??? for unknown values

\section{Discussion}
There are continuing efforts to reduce the impact of root vulnerabilities, both in Android and more widely.
SEAndroid~\cite{Smalley2013} which is included in Android from version ???~\cite{TODO} claimed to prevent some root vulnerabilities and to reduce the impact of others.
Capability based enforcement systems such as Capsicum~\cite{Watson2010} substantially reduce the capabilities that an exploit has to try and gain increased privilege with.
When Capsicum is included in Linux~\cite{TODO} and hence in Android, it could be used to place fine grained restrictions on system daemons, preventing vulnerabilities becoming root vulnerabilities.

>>>>

\section{Discussion}
There are continuing efforts to reduce the impact of root vulnerabilities, both in Android and more widely.
SEAndroid~\cite{Smalley2013} which is included in Android from version XXX~\cite{TODO} claimed to prevent some root vulnerabilities and to reduce the impact of others.
Capability based enforcement systems such as Capsicum~\cite{Watson2010} substantially reduce the capabilities that an exploit has to try and gain increased privilege with.
When Capsicum is included in Linux~\cite{TODO} and hence in Android, it could be used to place fine grained restrictions on system daemons, preventing vulnerabilities becoming root vulnerabilities.
